paper

### 2019-01-10 Report/paper.tex
push paper
updates

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines

@@

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{paper}

@@

\begin{abstract}
    In this report we explore ways to automatically analyze ICLS and CSCL
papers to gain an understanding of the community formed by conferences
participants and of the research being conducted within the community.
After describing how to extract data from the original dataset we we
derive insights into the community using social network analysis and
{[}Nour: NLP etc{]}. We discover patterns of collaboration between
participants, their migration and the global spread of the community.
{[}Something about the insights in keywords/NLP/Co-Citation{]}
\end{abstract}
    \hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\begin{itemize}
\tightlist
\item
  the institutions and countries dominant in the conferences
\item
  the differences between ICLS and CSCL with respect to citations,
  contributors and publications
\item
  first insight into changes of the years with respect to citations,
  contributors and publications
\item
  collaboration network patterns with respect to countries, institutions
  and authors
\item
  the migration of participants across institutions
\item
  \ldots{} {[}Nour{]}
\end{itemize}

@@

    \hypertarget{data-processing}{%
\section{Data Processing}\label{data-processing}}

@@

    \hypertarget{processing-the-metadata}{%
\subsection{Processing the Metadata}\label{processing-the-metadata}}

We extract the metadata from the xml files using the \emph{lxmltree}
python library. We associate the contents of each xml tag to a column in
csv file. As the xml files do not exactly follow the xml standard, we
handle errors by iteratively parsing the xml tree. For some files, the
section containing the keywords is malformed which can not be handled by
the parser. This is remedied by using regular expressions to match the
section contains the keywords. To each file we associate the name of the
source file and the order in which an author name occurs in the xml
file. Each author is associated one line in the XML file. From the
associated citation string we add to the first part of the citation
containing the author names, year and title. which we use to identify
references in other papers to that paper. Then we add a shortened
version of author names (i.e.~West, R.) by considering the author order.
Note that the short name extracted from the citation and the
corresponding long name (Robert West) in the metadata do at times not
match up. Thus the author order listed in the citation string does not
always correspond to the author order listed in the metadata. After
extraction, we clean the data by unifying names, as slight spelling
differences exist within the same author name (i.e.~Robert West, Robert
A. West). When unifying the names we need to make sure to not overmerge
by labeling to different authors as having the same name. First, we use
a strict condition to catch small differences in names, such as an extra
middle name. This is done by splitting up names into substrings based on
whitespace and commas. For two names in the dataset we check whether the
intersection of their sets of substrings contains at least 2 names of
length at least 3. If the condition is met we consider these two names
to be identical, and add the mapping from one name to the other to a
dictionary. Once all tuples of names (s.t. the first name appears before
the second one in order) are checked and added to the dictionary we
unify the names. Using this method we reduce the number of authors in
the dataset from 1951 down to 1879. Further, to merge names with
misspellings or people that use nicknames (Christian vs Chris) and avoid
over-merging we consider only names of authors that have similar
collaboration patterns. To do this we build the graph of co-authors and
check names of authors that are in the same neighborhood of a node on
the graph (see methodology for further details). Then we use the
\emph{difflib} library to check for similarity of two strings and
consider a name to belong to the same person if they reach the threshold
of 0.8. Again names considered to belong to the same person are added to
the mapping dictionary which is then applied to all names. This method
again reduces the number of authors in the dataset from 1879 to 1951.

    \hypertarget{handling-of-pdf-data}{%
\subsection{Handling of pdf data}\label{handling-of-pdf-data}}

To extract information from the papers themselves we need to first
extract the text from the pdfs. Various parsers performing this task
exist. However, parsers such as pdfminer, PyPDF2 that claim to be able
to extract the text as well as metadata from papers have not been kept
up to date, which leads to issues with dependencies. We found that the
most reliable parser is \emph{poppler} \cite{poppler} which can be
installed and then used via the command line to extract the text
contained in the pdfs to \emph{txt} format. All methods describing how
to extract data from the papers work on the extracted \emph{txt} files.
The characters contained in the \emph{txt} files are not all encoded
uniformly, which means that characters that look the same to humans may
be encoded in different way . Hence, for many applications we need to
unify the formating. This is done using the \emph{unicodedata} module
and setting converting all characters to `Normal Form Composed' form .

@@

\hypertarget{extracting-the-papers-cited-by-a-paper}{%
\subsection{Extracting the papers cited by a
paper}\label{extracting-the-papers-cited-by-a-paper}}

@@

    \hypertarget{extracting-institution-and-location}{%
\subsection{Extracting Institution and
Location}\label{extracting-institution-and-location}}

@@

\hypertarget{approach-1}{%
\subsubsection{Approach 1}\label{approach-1}}

@@

\hypertarget{approach-2}{%
\subsubsection{Approach 2}\label{approach-2}}

@@

    \hypertarget{keywords-extraction}{%
\subsection{Keywords extraction}\label{keywords-extraction}}

    \hypertarget{text-preprocessing}{%
\subsubsection{Text preprocessing}\label{text-preprocessing}}

@@

    \begin{itemize}
\tightlist
\item
  \textbf{\emph{TF-IDF}}: Tf--idf is one of the most popular
  term-weighting schemes today, in information retrieval, tf--idf or
  TFIDF, short for term frequency--inverse document frequency, is a
  numerical statistic that is intended to reflect how important a word
  is to a document in a collection or corpus. It is often used as a
  weighting factor in searches of information retrieval, text mining,
  and user modeling. The tf--idf value increases proportionally to the
  number of times a word appears in the document and is offset by the
  number of documents in the corpus that contain the word, which helps
  to adjust for the fact that some words appear more frequently in
  general.
\end{itemize}

@@

    We wanted then to know what are the trends of words for each specific
year, so we select distinct words for each year, it means that we select
for each year the words that were present for that year and never for
the others. We get the graph below. As we can see from the graph, the
most used word in the papers, more than 10\% of 2015 papers uses the
word `peer', more than 6\% of the papers uses the words `building',
`embodied' in 2016. In 2017 the most frequent keyword on is `reponsive'
and in 2018 `tools' is present with more than 6\%.

    \hypertarget{methodology-find-better-section-head..}{%
\section{Methodology {[}find better section
head..{]}}\label{methodology-find-better-section-head..}}

    \hypertarget{document-clustering}{%
\subsection{Document Clustering}\label{document-clustering}}

@@

\hypertarget{approach-1-natural-langage-processing-nlp}{%
\subsubsection{Approach 1 : Natural Langage Processing
(NLP)}\label{approach-1-natural-langage-processing-nlp}}

\hypertarget{baseline-tf-idf-combined-with-k-means}{%
\paragraph{Baseline : TF-IDF combined with
K-means}\label{baseline-tf-idf-combined-with-k-means}}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_30_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \hypertarget{second-method-average-of-glove-vectors-combined-with-k-means}{%
\paragraph{Second method : Average of GloVe vectors combined with
K-means}\label{second-method-average-of-glove-vectors-combined-with-k-means}}

@@

\textbf{\emph{GloVe}}, coined from Global Vectors, is a model for
distributed word representation. The model is an unsupervised learning
algorithm for obtaining vector representations for words. Training is
performed on aggregated global word-word co-occurrence statistics from a
corpus (Wikipedia), and the resulting representations showcase
interesting linear substructures of the word vector space. It is
developed as an open-source project at Stanford.{[}1{]}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_32_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \hypertarget{third-method-weighted-average-of-tf-idf-glove-combined-with-k-means}{%
\paragraph{Third method : Weighted average of TF-IDF + GloVe combined
with
K-means}\label{third-method-weighted-average-of-tf-idf-glove-combined-with-k-means}}

@@

\textbf{PCA} is a statistical procedure that uses an orthogonal
transformation to convert a set of observations of possibly correlated
variables (entities each of which takes on various numerical values)
into a set of values of linearly uncorrelated variables called principal
components. If there are \textbf{\emph{n}} observations with ****p****
variables, then the number of distinct principal components is
\textbf{\emph{min(n-1,p)}}. This transformation is defined in such a way
that the first principal component has the largest possible variance
(that is, accounts for as much of the variability in the data as
possible), and each succeeding component in turn has the highest
variance possible under the constraint that it is orthogonal to the
preceding components. The resulting vectors (each being a linear
combination of the variables and containing n observations) are an
uncorrelated orthogonal basis set. PCA is sensitive to the relative
scaling of the original variables.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \hypertarget{approach-2-references-network-analysis}{%
\subsubsection{Approach 2 : References Network
Analysis}\label{approach-2-references-network-analysis}}

@@

    \hypertarget{first-reference-graph-intersection-between-referenced-documents}{%
\paragraph{First reference graph : Intersection between referenced
documents}\label{first-reference-graph-intersection-between-referenced-documents}}

Our first graph is constructed using the references of each document. It
is constructed as follow, for each two documents, if there is an
intersection between the references of both documents then there is a
link. The weights of the edges are the length of the intersection set.
The intuition behind is that the more the weight is high, the more the
documents are likely to be about the same subjects since they are citing
the same documents. From this graph, we create a subgraph of it, we
filter the edges keeping only those who have a weight strictly higher
than 3. It means that, each node of the subgraph, is related to at least
one other node with 4 same documents referenced.

@@

    \hypertarget{second-graph-relations-between-references}{%
\paragraph{Second graph: Relations between
references}\label{second-graph-relations-between-references}}

@@

@@

    \hypertarget{third-graph-title-to-find}{%
\paragraph{Third graph: ??? Title to
find}\label{third-graph-title-to-find}}

@@

    \hypertarget{co-authorship}{%
\subsection{Co-authorship}\label{co-authorship}}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
        \caption{One of the connected components of the co-authorship graph}
        \label{fig_plot}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_49_0.png}\end{center}
        \caption{Largest Component}
        \label{author_collab_large}
    \end{figure}

    Focusing in on the authors is not the only way to interpret the
co-authorship graph. One should also consider the overall structure of
the graph. As graph is not connected, and contains one large main
component with 1141 authors and 208 very small components with less than
25 authors in them we focus on analyzing the structure of the main
component of the graph. First we aim to detect sub-communities within
the graph. Modularity is one measure used to find such communities. It
measures the connection strength within a community relative to the
strength of outgoing connections. Networks with high modularity have
dense connections between the nodes within modules but sparse
connections between nodes in different modules. A non-parametric
algorithm for community detection is the Louvain Method
\cite{blondel2008fast}. We used the implementation of Thomas Aynaud
\cite{louvain}. This gives a good partitioning of the graph into 26
communities of median size 42.84. This is quite a large number of
communities, so we consider an alternative way to yield bigger
partitions. An alternate way to find subcommunities is to look at
normalized cuts, which partition the nodes into groups with many
within-group connections and relatively few between-group connections.
The advantage of this method is that we can choose how many cuts to
make, and we are thus able to define the size of subcommunities. Finding
normalized cuts in a graph can be done using \emph{sklearns} spectral
clustering algorithm by passing it the adjacency matrix of the graph.
With this method we are able to neatly separate the main component graph
in three large communities. We note that the clusters found using method
one are contained in the clusters found by method 2. See Figure \ref{}
and Figure \ref{}.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{unigraph}
    \end{figure}

@@

    \hypertarget{creating-interactive-visualizations}{%
\subsection{Creating Interactive
Visualizations}\label{creating-interactive-visualizations}}

@@

    \hypertarget{results}{%
\section{Results}\label{results}}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
        \caption{Distribution of papers published over the years}
        \label{fig1}
    \end{figure}

    \hypertarget{community-composition-structure}{%
\subsection{Community Composition \&
Structure}\label{community-composition-structure}}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{figrep}
    \end{figure}

    \hypertarget{collaboration}{%
\subsubsection{Collaboration}\label{collaboration}}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
        \caption{Collaborative papers between countries}
        \label{figcollab}
    \end{figure}

    \hypertarget{movement-of-particpants}{%
\subsubsection{Movement of particpants}\label{movement-of-particpants}}

@@

    \hypertarget{research-topics-in-the-community}{%
\subsection{Research topics in the
Community}\label{research-topics-in-the-community}}

@@

    \hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

>>>>

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines
    \usepackage{mathrsfs}

@@

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatibility definitions
    \def\gt{>}
    \def\lt{<}
    \let\Oldtex\TeX
    \let\Oldlatex\LaTeX
    \renewcommand{\TeX}{\textrm{\Oldtex}}
    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
    % Document parameters
    % Document title
    \title{paper}

@@

\begin{abstract}
    In this report we explore ways to automatically analyze ICLS and CSCL
papers to gain an understanding of the community formed by conferences
participants and of the research being conducted within the community.
After describing how to extract data from the original dataset we derive
insights into the community using social network analysis, natural
language processing and text mining. We discover patterns of
collaboration between participants, their migration and the global
spread of the community. We also extracted keywords and find clusters of
referenced papers and documents within the conferences.
\end{abstract}
    \section{Introduction}\label{introduction}

@@

\begin{itemize}
\tightlist
\item
  the institutions and countries dominant in the conferences
\item
  the differences between ICLS and CSCL with respect to citations,
  contributors and publications
\item
  first insight into changes of the years with respect to citations,
  contributors and publications
\item
  collaboration network patterns with respect to countries, institutions
  and authors
\item
  the migration of participants across institutions
\item
  trends of keywords over the years
\item
  trends of citations and evolution of the number of documents from 1977
  until 2018
\item
  clusters of the cited documents
\item
  clusters of the papers written within the conferences
\end{itemize}

@@

    \section{Data Processing}\label{data-processing}

@@

    \subsection{Processing the Metadata}\label{processing-the-metadata}

We extract the metadata from the xml files using the \emph{lxmltree}
python library. We associate the contents of each xml tag to a column in
csv file. As the xml files do not exactly follow the xml standard, we
handle errors by iteratively parsing the xml tree. For some files, the
section containing the keywords is malformed which can not be handled by
the parser. This is remedied by using regular expressions to match the
section contains the keywords. To each file we associate the name of the
source file and the order in which an author name occurs in the xml
file. Each author is associated one line in the XML file. From the
associated citation string we add to the first part of the citation
containing the author names, year and title. which we use to identify
references in other papers to that paper. Then we add a shortened
version of author names (i.e. West, R.) by considering the author order.
Note that the short name extracted from the citation and the
corresponding long name (Robert West) in the metadata do at times not
match up. Thus the author order listed in the citation string does not
always correspond to the author order listed in the metadata. After
extraction, we clean the data by unifying names, as slight spelling
differences exist within the same author name (i.e. Robert West, Robert
A. West). When unifying the names we need to make sure to not overmerge
by labeling to different authors as having the same name. First, we use
a strict condition to catch small differences in names, such as an extra
middle name. This is done by splitting up names into substrings based on
whitespace and commas. For two names in the dataset we check whether the
intersection of their sets of substrings contains at least 2 names of
length at least 3. If the condition is met we consider these two names
to be identical, and add the mapping from one name to the other to a
dictionary. Once all tuples of names (s.t. the first name appears before
the second one in order) are checked and added to the dictionary we
unify the names. Using this method we reduce the number of authors in
the dataset from 1951 down to 1879. Further, to merge names with
misspellings or people that use nicknames (Christian vs Chris) and avoid
over-merging we consider only names of authors that have similar
collaboration patterns. To do this we build the graph of co-authors and
check names of authors that are in the same neighborhood of a node on
the graph (see methodology for further details). Then we use the
\emph{difflib} library to check for similarity of two strings and
consider a name to belong to the same person if they reach the threshold
of 0.8. Again names considered to belong to the same person are added to
the mapping dictionary which is then applied to all names. This method
again reduces the number of authors in the dataset from 1879 to 1951.

    \subsection{Handling of pdf data}\label{handling-of-pdf-data}

To extract information from the papers themselves we need to first
extract the text from the pdfs. Various parsers performing this task
exist. However, parsers such as pdfminer, PyPDF2 that claim to be able
to extract the text as well as metadata from papers have not been kept
up to date, which leads to issues with dependencies. We found that the
most reliable parser is \emph{poppler} \cite{poppler} which can be
installed and then used via the command line to extract the text
contained in the pdfs to \emph{txt} format. All methods describing how
to extract data from the papers work on the extracted \emph{txt} files.
The characters contained in the \emph{txt} files are not all encoded
uniformly, which means that characters that look the same to humans may
be encoded in different way . Hence, for many applications we need to
unify the formating. This is done using the \emph{unicodedata} module
and setting converting all characters to 'Normal Form Composed' form .

@@

\subsection{Extracting the papers cited by a
paper}\label{extracting-the-papers-cited-by-a-paper}

@@

    \subsection{Extracting Institution and
Location}\label{extracting-institution-and-location}

@@

\subsubsection{Approach 1}\label{approach-1}

@@

\subsubsection{Approach 2}\label{approach-2}

@@

    \subsection{Keywords extraction}\label{keywords-extraction}

    \subsubsection{Text preprocessing}\label{text-preprocessing}

@@

    \begin{itemize}
\tightlist
\item
  \textbf{\emph{TF-IDF}}: Tf--idf is one of the most popular
  term-weighting schemes today, in information retrieval, tf--idf or
  TFIDF, short for term frequency--inverse document frequency, is a
  numerical statistic that is intended to reflect how important a word
  is to a document in a collection or corpus. It is often used as a
  weighting factor in searches of information retrieval, text mining,
  and user modeling. The tf--idf value increases proportionally to the
  number of times a word appears in the document and is offset by the
  number of documents in the corpus that contain the word, which helps
  to adjust for the fact that some words appear more frequently in
  general \cite{Tf-idf}
\end{itemize}

@@

    We wanted then to know what are the trends of words for each specific
year, so we select distinct words for each year, it means that we select
for each year the words that were present for that year and never for
the others. We get the graph below. As we can see from the graph, the
most used word in the papers, more than 10\% of 2015 papers uses the
word 'peer', more than 6\% of the papers uses the words 'building',
'embodied' in 2016. In 2017 the most frequent keyword on is 'reponsive'
and in 2018 'tools' is present with more than 6\%.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_28_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \section{Methodology {[}find better section
head..{]}}\label{methodology-find-better-section-head..}

    \subsection{Document Clustering}\label{document-clustering}

@@

\subsubsection{Approach 1 : Natural Langage Processing
(NLP)}\label{approach-1-natural-langage-processing-nlp}

\paragraph{Baseline : TF-IDF combined with
K-means}\label{baseline-tf-idf-combined-with-k-means}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \paragraph{Second method : Average of GloVe vectors combined with
K-means}\label{second-method-average-of-glove-vectors-combined-with-k-means}

@@

\textbf{\emph{GloVe}}, coined from Global Vectors, is a model for
distributed word representation. The model is an unsupervised learning
algorithm for obtaining vector representations for words. Training is
performed on aggregated global word-word co-occurrence statistics from a
corpus (Wikipedia), and the resulting representations showcase
interesting linear substructures of the word vector space. It is
developed as an open-source project at Stanford.\cite{GloVe}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \paragraph{Third method : Weighted average of TF-IDF + GloVe combined
with
K-means}\label{third-method-weighted-average-of-tf-idf-glove-combined-with-k-means}

@@

\textbf{PCA} is a statistical procedure that uses an orthogonal
transformation to convert a set of observations of possibly correlated
variables (entities each of which takes on various numerical values)
into a set of values of linearly uncorrelated variables called principal
components. If there are \textbf{\emph{n}} observations with ****p****
variables, then the number of distinct principal components is
\textbf{\emph{min(n-1,p)}}. This transformation is defined in such a way
that the first principal component has the largest possible variance
(that is, accounts for as much of the variability in the data as
possible), and each succeeding component in turn has the highest
variance possible under the constraint that it is orthogonal to the
preceding components. The resulting vectors (each being a linear
combination of the variables and containing n observations) are an
uncorrelated orthogonal basis set. PCA is sensitive to the relative
scaling of the original variables \cite{PCA}.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \subsubsection{Approach 2 : References Network
Analysis}\label{approach-2-references-network-analysis}

@@

    \paragraph{First reference graph : Intersection between referenced
documents}\label{first-reference-graph-intersection-between-referenced-documents}

Our first graph is constructed using the references of each document. It
is constructed as follow, for each two documents, if there is an
intersection between the references of both documents then there is a
link. The weights of the edges are the length of the intersection set.
The intuition behind is that the more the weight is high, the more the
documents are likely to be about the same subject since they are citing
the same documents. From this graph, we create a subgraph of it, we
filter the edges keeping only those who have a weight strictly higher
than 3. It means that, each node of the subgraph, is related to at least
one other node with 4 same documents referenced.

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}212}]:} <IPython.core.display.HTML object>
\end{Verbatim}

@@

    \paragraph{Second graph: Relations between
references}\label{second-graph-relations-between-references}

@@

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}103}]:} <IPython.core.display.HTML object>
\end{Verbatim}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_44_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

    \paragraph{Third graph: exploratory references
graph}\label{third-graph-exploratory-references-graph}

@@

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}105}]:} <IPython.core.display.HTML object>
\end{Verbatim}

    \subsection{Co-authorship}\label{co-authorship}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_50_0.png}\end{center}
        \caption{One of the connected components of the co-authorship graph}
        \label{fig_plot}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
        \caption{Largest Component}
        \label{author_collab_large}
    \end{figure}

    Focusing in on the authors is not the only way to interpret the
co-authorship graph. One should also consider the overall structure of
the graph. As graph is not connected, and contains one large main
component with 1141 authors and 208 very small components with less than
25 authors in them we focus on analyzing the structure of the main
component of the graph. First we aim to detect sub-communities within
the graph. Modularity is one measure used to find such communities. It
measures the connection strength within a community relative to the
strength of outgoing connections. Networks with high modularity have
dense connections between the nodes within modules but sparse
connections between nodes in different modules. A non-parametric
algorithm for community detection is the Louvain Method
\cite{blondel2008fast}. We used the implementation of Thomas Aynaud
\cite{louvain}. This gives a good partitioning of the graph into 26
communities of median size 42.84. This is quite a large number of
communities, so we consider an alternative way to yield bigger
partitions. An alternate way to find subcommunities is to look at
normalized cuts, which partition the nodes into groups with many
within-group connections and relatively few between-group connections.
The advantage of this method is that we can choose how many cuts to
make, and we are thus able to define the size of subcommunities. Finding
normalized cuts in a graph can be done using \emph{sklearns} spectral
clustering algorithm by passing it the adjacency matrix of the graph.
With this method we are able to neatly separate the main component graph
in three large communities. We note that the clusters found using method
one are contained in the clusters found by method 2. See Figure
\ref{Louvain} and Figure \ref{normalized}.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_53_0.png}\end{center}
        \caption{Subcommunities by Louvain}
        \label{Louvain}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
        \caption{Subcommunities via normalized cuts}
        \label{normalized}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_56_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{unigraph}
    \end{figure}

@@

    \subsection{Creating Interactive
Visualizations}\label{creating-interactive-visualizations}

@@

    \section{Results}\label{results}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
        \caption{Distribution of papers published over the years}
        \label{fig1}
    \end{figure}

    \subsection{Community Composition \&
Structure}\label{community-composition-structure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{figrep}
    \end{figure}

    \subsubsection{Collaboration}\label{collaboration}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
        \caption{Collaborative papers between countries}
        \label{figcollab}
    \end{figure}

    \subsubsection{Movement of particpants}\label{movement-of-particpants}

@@

    \subsection{Research topics in the
Community}\label{research-topics-in-the-community}

@@

    \subsection{Clustering and referecences graphs
results}\label{clustering-and-referecences-graphs-results}

The distribution of referenced publications years are plotted in the
graph below. We can see from the graph that there is a kind of a trend,
each two, three years there is a pick of documents referenced followed
by a two or three years of stagnancy. We can also notice that
throughouts the year each pick is higher than the older one, which can
be explained by the fact that The International Society of the Learning
Sciences community is investigating more and more tools to facilitate
learning over the years.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    Since the number of documents is increasing over the years, we also
wanted to investigate more if the relevance of all the documents
published is increasing too. Using Pagerank algorithm and the In-degree
of each nodes to get the most influancial documents referenced of the
citation graph that we constructed (graph3) before. We filtered the
first 100 documents and then contructed a histogram of the counts. We
obtain the figure below:

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_70_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    We can see that in the top 100 cited documents more than 12\% are from
2006, 8\% are from 2013, 6\% from 2014... We can not say that we have
the same trend as before, and the relevance of the documents is
increasing in the same way than with the number of publications but what
we can say is that more than 50\% of the most cited documents are from
2006 until 2016, we is 10 years. The other half is between 1977 until
2005 which represents more than 25 years. On top of that, 2016 is the
most important year in term of publications and maybe some documents did
not have enough time to be cited yet.

    The top 10 of the most influencial and most important referenced papers
are the following:

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    We also noticed from the first graph that some documents were more
likely to cited together. We can say that the more two documents are
likely to cited together the more it is probable that both documents are
about the same subject From the table below we can also notice that some
papers cites like to cite the same authors together, which is logic in a
sense, because if some authors always treat about the same subjects then
they are experts in that field and a lot of their publications are
relevant and can be cited together.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_75_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    Using this graph, we also want to extract if there are some clusters of
papers cited together. As we explained before, we run strongly connected
algorithm to check if some cited documents are more likely to cited
together, and this will give us clusters of cited documents that are
more likely to be about the same subjects. We can visualise one cluster,
the most important one.

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}176}]:}                                                                                                                                                                                                                                                                                                                           Documents
          cluster 4 0                                                                                                                                                                                                                                  schommer, m. (1990). effects of beliefs about the nature of knowledge on comprehension
                    1                                                                                                                                                                          stathopoulou, c., \& vosniadou, s. (2007). exploring the relationship between physics-related epistemological beliefs and physics understanding
                    2                                                                                                                                                                 hofer, b. k., \& pintrich, p. r. (1997). the development of epistemological theories: beliefs about knowledge and knowing and their relation to learning
                    3                                                                                                                                                             chinn, c. a., buckland, l. a., \& samarapungavan, a. l. a. (2011). expanding the dimensions of epistemic cognition: arguments from philosophy and psychology
          cluster 3 0  yoon, s., klopfer, e., wang, j., sheldon, j., wendel, d., schoenfeld, i., scheintaub, h., \& reider, d. (2013). designing to improve biology understanding through complex systems in high school classrooms: no simple matter! in the proceedings of the computer supported collaborative learning, madison, wisconsin
                    1                                                                                                                                                             ertmer, p.a., ottenbreit-leftwich, a.t., sendurur, e., \& sendurur, p. (2012). teacher beliefs and technology integration practices: a critical relationship
                    2                                                                                                                                                                                                                                                                                          epstein, j. (2008). 'why model
                    3                                                                                                                                                                                        national research council. (2012). education for life and work: developing transferable knowledge and skills in the 21st century
                    4                                                                                                                                                                                                       thompson, j, windschitl, m., \& braaten, m. (2013). developing a theory of ambitious early-career teacher practice
                    5                                                                                                                                                                                      desimone, l. (2009). improving impact studies of teachers’ professional development: toward better conceptualizations and measures
                    6                                                                     yoon, s., koehler-yom, j., anderson, e., lin, j., \& klopfer, e. (accepted). using an adaptive expertise lens to understand the quality of teachers’ classroom implementation of computer-supported complex systems curricula in high school science
                    7                                                                                                                         mueller, j., wood, e., willoughby, t., ross, c., \& specht, j. (2008). identifying discriminating variables between teachers who fully integrate computers and teachers with limited integration
